Simulation Results

### 2020-05-01 Simulation Results/Simulation Results.Rmd
sim results

@@

  expression_string <- combined_results$expression[[7]]
  expression_string
  get_method_name <- function(expression_string) {
    string <- as.character(expression_string)[1]
    string
    if (string == "run.jags") {
      method <- "JAGS"
    } else if (string == "bugs") {
      method <- "OpenBUGS"
    } else if (string == "nimbleMCMC") {
      method <- "Nimble"
    } else if (string == "stan") {
      method <- "STAN"
    } else if (string == "mcmc") {
      method <- "Greta"
    } else if (string == "stan_model") {
      method <- "STAN Compile"
    }
    method
  }

@@

exp_gamma_results <- exp_gamma_bench_files %>% 
  combine_bench("exponential_gamma")
normal_gamma_tau_results <- normal_gamma_tau_bench_files %>%
  combine_bench("normal_gamma_tau")
normal_normal_results <- normal_normal_bench_files %>%
  combine_bench("normal_normal")
beta_bernoulli_results <- beta_bernoulli_bench_files %>%
  combine_bench("beta_bernoulli")
beta_binomial_results <- beta_binomial_bench_files %>%
  combine_bench("beta_binomial")
poisson_gamma_results <- poisson_gamma_bench_files %>%
  combine_bench("poisson_gamma")
poisson_gamma_results

x <- readRDS(bench_files[3])
x
```

>>>>

hierarchical_beta_binomial_bench_files <- c(
  here("Simulation Results", "hierarchical-models", "beta-binomial", "hierarchical-beta-binomial-results.rds"),
  here("Simulation Results", "hierarchical-models", "beta-binomial", "hierarchical-beta-binomial-results-greta.rds"),
  here("Simulation Results", "hierarchical-models", "beta-binomial", "hierarchical-beta-binomial-results-stan.rds")
)

hierarchical_full_beta_binomial_bench_files <- c(
  here("Simulation Results", "hierarchical-models", "full-beta-binomial", "hierarchical-full-beta-binomial-results.rds"),
  here("Simulation Results", "hierarchical-models", "full-beta-binomial", "hierarchical-full-beta-binomial-results-greta.rds"),
  here("Simulation Results", "hierarchical-models", "full-beta-binomial", "hierarchical-full-beta-binomial-results-stan.rds")
)

hierarchical_logistic_regression_bench_files <- c(
  here("Simulation Results", "regression-models", "hierarchical-logistic-regression",  "hierarchical-logistic-regression-results.rds"),
  here("Simulation Results", "regression-models", "hierarchical-logistic-regression",  "hierarchical-logistic-regression-results-greta.rds"),
  here("Simulation Results", "regression-models", "hierarchical-logistic-regression",  "hierarchical-logistic-regression-results-stan.rds")
)

linear_regression_bench_files <- c(
  here("Simulation Results", "regression-models", "linear-regression",  "linear-regression-results.rds"),
  here("Simulation Results", "regression-models", "linear-regression",  "linear-regression-results-greta.rds"),
  here("Simulation Results", "regression-models", "linear-regression",  "linear-regression-results-stan.rds")
)

logistic_regression_bench_files <- c(
  here("Simulation Results", "regression-models", "logistic-regression",  "logistic-regression-results.rds"),
  here("Simulation Results", "regression-models", "logistic-regression",  "logistic-regression-results-greta.rds"),
  here("Simulation Results", "regression-models", "logistic-regression",  "logistic-regression-results-stan.rds")
)

poisson_regression_bench_files <- c(
  here("Simulation Results", "regression-models", "poisson-regression",  "poisson-regression-results.rds"),
  here("Simulation Results", "regression-models", "poisson-regression",  "poisson-regression-results-greta.rds"),
  here("Simulation Results", "regression-models", "poisson-regression",  "poisson-regression-results-stan.rds")
)

cox_exponential_bench_files <- c(
  here("Simulation Results", "survival-models", "cox-exponential-results.rds"),
  here("Simulation Results", "survival-models", "cox-exponential-results-greta.rds"),
  here("Simulation Results", "survival-models", "cox-exponential-results-stan.rds")
)

files <- logistic_regression_bench_files

@@

  # expression_string <- combined_results$expression[[7]]
  # expression_string
  get_method_name <- function(expression_string) {
    string <- as.character(expression_string)[1]
    string
    if (string == "run.jags") {
      method <- "JAGS"
    } else if (string == "bugs") {
      method <- "OpenBUGS"
    } else if (string == "nimbleMCMC") {
      method <- "Nimble"
    } else if (string == "stan") {
      method <- "STAN"
    } else if (string == "mcmc") {
      method <- "Greta"
    } else if (string == "stan_model") {
      method <- "STAN Compile"
    }
    method
  }

@@

combine_bench_indiv <- function(files, model_name) {
  combined_results <- files %>% map_dfr(~ readRDS(.))
  combined_results

  # expression_string <- combined_results$expression[[7]]
  # expression_string
  get_method_name <- function(expression_string) {
    string <- as.character(expression_string)[1]
    string
    if (string == "run.jags") {
      method <- "JAGS"
    } else if (string == "bugs") {
      method <- "OpenBUGS"
    } else if (string == "nimbleMCMC") {
      method <- "Nimble"
    } else if (string == "stan") {
      method <- "STAN"
    } else if (string == "mcmc") {
      method <- "Greta"
    } else if (string == "stan_model") {
      method <- "STAN Compile"
    }
    method
  }

  times <- combined_results$time[[1]]

  time_results <- combined_results$time

  names(time_results) <- method_names

  get_iterations_for_method <- function(times, name) {
    tibble(
      method = name,
      time = times,
      model_name = model_name
    )
  }

  res <- time_results %>% imap_dfr(get_iterations_for_method)

  # 
  # method_mean <- combined_results$time %>% map_dbl(~ mean(.))
  # method_sd <- combined_results$time %>% map_dbl(~ sd(.))
  # 
  # results <- combined_results %>% 
  #   mutate(method = method_names, mean = method_mean, sd = method_sd, 
  #          model_name = model_name) %>% 
  #   select(method, mean, median, min, sd, n_itr, model_name)
  # 
  # rows_to_keep <- results$method %>% unique() %>% 
  #   map_dbl(~ which(results$method == .)[1])
  # 
  # results <- results[rows_to_keep,] %>% 
  #   arrange(method)

  res

# exp_gamma_results <- exp_gamma_bench_files %>% 
#   combine_bench("exponential_gamma")
# normal_gamma_tau_results <- normal_gamma_tau_bench_files %>%
#   combine_bench("normal_gamma_tau")
# normal_normal_results <- normal_normal_bench_files %>%
#   combine_bench("normal_normal")
# beta_bernoulli_results <- beta_bernoulli_bench_files %>%
#   combine_bench("beta_bernoulli")
# beta_binomial_results <- beta_binomial_bench_files %>%
#   combine_bench("beta_binomial")
# poisson_gamma_results <- poisson_gamma_bench_files %>%
#   combine_bench("poisson_gamma")
# hier_beta_binomial_results <- hierarchical_beta_binomial_bench_files %>%
#   combine_bench("hierarchical_beta_binomial")
# hier_full_bb_results <- hierarchical_full_beta_binomial_bench_files %>%
#   combine_bench("hierarchical_full_beta_binomial")
# hier_log_reg_results <- hierarchical_logistic_regression_bench_files %>%
#   combine_bench("hierarchical_logistic_regression")
# linear_reg_results <- linear_regression_bench_files %>% 
#   combine_bench("linear regression")
# logistic_reg_results <- logistic_regression_bench_files %>% 
#   combine_bench("logistic regression")
# poisson_reg_results <- poisson_regression_bench_files %>% 
#   combine_bench("poisson regression")

exp_gamma_results <- exp_gamma_bench_files %>% 
  combine_bench_indiv("exponential_gamma")
normal_gamma_tau_results <- normal_gamma_tau_bench_files %>%
  combine_bench_indiv("normal_gamma_tau")
normal_normal_results <- normal_normal_bench_files %>%
  combine_bench_indiv("normal_normal")
beta_bernoulli_results <- beta_bernoulli_bench_files %>%
  combine_bench_indiv("beta_bernoulli")
beta_binomial_results <- beta_binomial_bench_files %>%
  combine_bench_indiv("beta_binomial")
poisson_gamma_results <- poisson_gamma_bench_files %>%
  combine_bench_indiv("poisson_gamma")
hier_beta_binomial_results <- hierarchical_beta_binomial_bench_files %>%
  combine_bench_indiv("hierarchical_beta_binomial")
hier_full_bb_results <- hierarchical_full_beta_binomial_bench_files %>%
  combine_bench_indiv("hierarchical_full_beta_binomial")
hier_log_reg_results <- hierarchical_logistic_regression_bench_files %>%
  combine_bench_indiv("hierarchical_logistic_regression")
linear_reg_results <- linear_regression_bench_files %>% 
  combine_bench_indiv("linear regression")
logistic_reg_results <- logistic_regression_bench_files %>% 
  combine_bench_indiv("logistic regression")
poisson_reg_results <- poisson_regression_bench_files %>% 
  combine_bench_indiv("poisson regression")

```

```{r}
# bench_results <- bind_rows(
#   exp_gamma_results,
#   normal_gamma_tau_results,
#   normal_normal_results,
#   beta_bernoulli_results, 
#   beta_binomial_results,
#   poisson_gamma_results,
#   hier_beta_binomial_results,
#   hier_full_bb_results,
#   hier_log_reg_results,
#   linear_reg_results,
#   logistic_reg_results,
#   poisson_reg_results
# )
# 
# bench_results
# 
# saveRDS(bench_results, file = "bench_results.RDS")

bench_results_indiv <- bind_rows(
  exp_gamma_results,
  normal_gamma_tau_results,
  normal_normal_results,
  beta_bernoulli_results, 
  beta_binomial_results,
  poisson_gamma_results,
  hier_beta_binomial_results,
  hier_full_bb_results,
  hier_log_reg_results,
  linear_reg_results,
  logistic_reg_results,
  poisson_reg_results
)

bench_results_indiv

bench_results_indiv <- bench_results_indiv %>% 
  filter(!(method == "STAN Compile" & time < 5))

saveRDS(bench_results_indiv, file = "bench_results_indiv.RDS")
```

```{r}
# bench_results %>% 
#   ggplot(aes(mean, color = method)) + 
#   geom_boxplot() + 
#   coord_flip() + 
#   xlim(0,90)
# 
# bench_results %>% 
#   ggplot(aes(mean, fill = method)) + 
#   geom_histogram() + 
#   facet_wrap(vars(method))
#   # coord_flip() + 
#   # xlim(0,90)

```

```{r}
bench_results_indiv <- readRDS("bench_results_indiv.RDS")

bench_results_indiv %>%
  ggplot(aes(time, color = method)) +
  geom_boxplot() +
  coord_flip() +
  xlim(0,90)

bench_results_indiv %>%
  ggplot(aes(time, fill = method)) +
  geom_histogram(aes(y = stat(density)), bins = 20) + 
  # xlim(0,100) +
  facet_wrap(vars(method))

bench_results_indiv %>%
  ggplot(aes(time, fill = method)) +
  geom_histogram(aes(y = stat(density)), bins = 20) + 
  xlim(0,100) +
  facet_wrap(vars(method))

```

##
